\begin{par}
Gorbach, N.S.  Validation and Inference of Structural Connectivity and Neural Dynamics with MRI data. 2018. ETH Z\"{u}rich Doctoral Thesis. \href{https://www.research-collection.ethz.ch/handle/20.500.11850/261734}{https://www.research-collection.ethz.ch/handle/20.500.11850/261734}. 
\end{par} \vspace{2em}
\begin{par}
Gorbach*, N.S. , Bauer*, S. and Buhmann, J.M., Scalable Variational Inference for Dynamical Systems. 2017a. Neural Information Processing Systems (NIPS). \href{https://papers.nips.cc/paper/7066-scalable-variational-inference-for-dynamical-systems.pdf}{https://papers.nips.cc/paper/7066-scalable-variational-inference-for-dynamical-systems.pdf}. arXiv paper:  \href{https://arxiv.org/abs/1705.07079}{https://arxiv.org/abs/1705.07079}.
\end{par} \vspace{2em}
\begin{par}
Bauer*, S. , Gorbach*, N.S. and Buhmann, J.M., Efficient and Flexible Inference for Stochastic Differential Equations. 2017b. Neural Information Processing Systems (NIPS). \href{https://papers.nips.cc/paper/7274-efficient-and-flexible-inference-for-stochastic-systems.pdf}{https://papers.nips.cc/paper/7274-efficient-and-flexible-inference-for-stochastic-systems.pdf}.
\end{par} \vspace{2em}
\begin{par}
Wenk, P., Gotovos, A., Bauer, S., Gorbach, N.S., Krause, A. and Buhmann, J.M., Fast Gaussian Process Based Gradient Matching for Parameters Identification in Systems of Nonlinear ODEs. 2018. In submission to Conference on Uncertainty in Artificial Intelligence (UAI). arxiv paper: \href{https://arXiv.org/abs/1804.04378}{https://arxiv.org/abs/1804.04378}.
\end{par} \vspace{2em}
\begin{par}
Calderhead, B., Girolami, M. and Lawrence. N.D., 2002. Accelerating Bayesian inference over nonlinear differential equation models. In Advances in Neural Information Processing Systems (NIPS) . 22.
\end{par} \vspace{3em}
\begin{par}
*The authors have contributed equally to their respective papers.
\end{par} 